Modeling a declining count variable

### 2023-07-30 text/08/declining-count-model.Rmd
More work on 2008 update pages

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Poisson regression
output: html_document
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.

>>>>

---
title: Modeling a declining count variable
author: Steve Simon
date: 2008-06-14
categories:
- Blog post
tags:
- Being updated
- Poisson regression
output: html_document
---
I've been working on an interesting project that requires Poisson
regression. A company sends out a mailing and gets a certain number of
telephone calls back on each of the days following. The number of phone
calls is typically (but not always) highest on the first day afterwards
and declines rapidly on successive days. I wanted to develop a simple
Poisson regression model for this data.
